PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-12-08 qfenv_paper/qf_environment.tex
Re-drafted intro (Incomplete)

Nevertheless, the evolution of the role of environment is a relatively
subtle effect and difficult to study.  Although the history of galaxies
prior to $z\sim 1$ appears to have been one of rapid assembly, since
that time the galaxy population has continued to evolve, but less
dramatically.

Although there are detectable changes in the population,
the major classes of galaxies existed at $z\sim 1$, in roughly the
same relative numbers as today (\citealt{bundy06a, borch06a,
taylor09a, Moustakas:2013aa}). Furthermore, at those redshifts we can also
detect the dependence of galaxy properties on environment, with lower
star-formation rate early-type galaxies populating the denser regions
(\citealt{cooper08a, patel09a, kovac10a}).
% Mention something about the build up of the red sequence?

The most dramatic change in galaxy properties during the past eight
billion years has been a remarkable decline in the star-formation rate
of galaxies in the Universe (\citealt{hopkins06a}).  This decline
appears dominated by decreases in the rates of star-formation of
individual galaxies (\citealt{Noeske:2007aa}). There is evidence that
a large fraction of the decline is associated with strongly
infrared-emitting starbursts (\citealt{bell05a, magnelli09a}).  The
decline does not appear to be due to a complete cessation of star
formation for a large fraction of the star-forming population, as
reflected in observations of the stellar mass function of quiescent
and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,
  borch06a, Moustakas:2013aa}).  These findings leave little room for
the participation of environmentally-driven cessation of star
formation in the global census of star-formation.  As \cite{cooper08a}
and others have pointed out, because the environmental dependence of
total star-formation rates at fixed redshift is relatively small,
environmentally effects are unlikely to cause the overall
star-formation rate decline.

Thus, the impact of environment on galaxy formation has to be
interpreted on top of the background of this overall decline affecting
galaxies in all environments. The most straightforward investigation
would be to directly determine the star-forming properties of galaxies
as a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
end their star formation over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the PRIism MUlti-object Survey (PRIMUS; \citealt{Coil:2011aa},
\citealt{Cool:2013aa}), the largest available redshift survey covering
the epochs between $0<z<1$.

>>>>

%Moreover, at $z < 1$ lower star-formation rate early-type galaxies are found populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).

Nevertheless, the evolution of the role of environment is a relatively subtle effect and must be interpreted on top of the changes in overall the galaxy population. For instance, the most dramatic change in galaxy properties during the past eight billion years has been the remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.

Furthermore, during this universal decline, the major classes of galaxies that have existed at $z \sim 1$ remain firmly in place since (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Although these classes have remained roughly the same relative number during this time, detailed observations of the stellar mass function find detectable changes in the quiescent and star-forming galaxy populations. There is a significant decline in the number density of massive/luminous star-forming galaxies accompanied by an increase in the number density of quiescent galaxies (\citealt{Bell:2004aa, Blanton:2006aa, bundy06a,  borch06a, Moustakas:2013aa}). The evolution of these two populations suggest a build up of the quiescent population caused by the cessation of star formation for some star-forming galaxies over time.

Of the numerous mechanisms that have been proposed to explain this cessation, some suggest that star-formation is quenched due to internal processes such as supernovae or active galactic nuclei that suppresses cold gas accretion (CITECITE). Other models suggest that environment dependent external processes such as ram-pressure stripping (CITE), strangulation (CITE), or harassment (CITE) contribute to the cessation. While discrepancies persist between these theoretical models and observations, many of the environment dependent processes have found observational support (CITECITE) suggesting that environment may play a role in ceasing star-formation.

%Nevertheless, the evolution of the role of environment is a relatively subtle effect and difficult to study.  Although the history of galaxies prior to $z\sim 1$ appears to have been one of rapid assembly, since that time the galaxy population has continued to evolve, but less dramatically. Although there are detectable changes in the population, the major classes of galaxies existed at $z\sim 1$, in roughly the same relative numbers as today (\citealt{bundy06a, borch06a, taylor09a, Moustakas:2013aa}). Furthermore, at those redshifts we can also detect the dependence of galaxy properties on environment, with lower star-formation rate early-type galaxies populating the denser regions (\citealt{cooper08a, patel09a, kovac10a}).

%The most dramatic change in galaxy properties during the past eight billion years has been a remarkable decline in the star-formation rate of galaxies in the Universe (\citealt{hopkins06a}). This decline  appears dominated by decreases in the rates of star-formation of individual galaxies (\citealt{Noeske:2007aa}). There is evidence that a large fraction of the decline is associated with strongly infrared-emitting starbursts (\citealt{bell05a, magnelli09a}). The decline does not appear to be due to a complete cessation of star formation for a large fraction of the star-forming population, as reflected in observations of the stellar mass function of quiescent and star-forming galaxies (\citealt{Blanton:2006aa, bundy06a,   borch06a, Moustakas:2013aa}).  These findings leave little room for the participation of environmentally-driven cessation of star formation in the global census of star-formation.  As \cite{cooper08a} and others have pointed out, because the environmental dependence of total star-formation rates at fixed redshift is relatively small, environmentally effects are unlikely to cause the overall star-formation rate decline.

%Thus, the impact of environment on galaxy formation has to be interpreted on top of the background of the build up of the red sequence during the overall decline in star-formation rate affecting galaxies in all environments. The most straightforward investigation would be to directly determine the star-forming properties of galaxies as a function of environment, stellar mass and redshift in a single, consistently analyzed data set.

In this paper we take the most straightforward investigation
by directly determining the star-forming properties of galaxies
as a function of environment, stellar mass and redshift in a single,
consistently analyzed data set. This analysis can reveal how galaxies
end their star formation over time, quantitatively establish the
contribution of environmental effects to the overall trends, and
reveal whether those trends happen equally in all environments.
However, such an analysis has not been done previously due to the lack
of sufficiently large samples. In this paper, we apply this approach
using the PRIism MUlti-object Survey (PRIMUS; \citealt{Coil:2011aa},
\citealt{Cool:2013aa}), the largest available redshift survey covering
the epochs between $0<z<1$.
